Data Dashboard

### 2020-01-27 analysis/05_market_simulator.Rmd
Added levels

```{r packages, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(flexdashboard)
library(plotly)
```

>>>>

```{r packages, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(flexdashboard)
library(plotly)
library(shiny)
library(here)
```

```{r load data}
intercept_mod <- readRDS(here('analysis', 'output', 'posterior_draws', 'intercept_noncentered.rds')) %>% 
  group_by(i) %>% 
  summarize(theta_mean = mean(Theta))
intercept_mod
#Levels (This is a guess):            Means:
#   1. Amnesty International          0.805
#   2. Greenpeace                     0.923
#   3. Oxfam                          0.620
#   4. Red Cross                      1.820
#   5. Environment                   -0.444
#   6. Human Rights                  -0.164
#   7. Refugee Relief                -0.582
#   8. Financially Transparent        1.080
#   9. Accountable                    1.130
#   10. Small wealthy donars         -0.376
#   11. Government Grants            -0.252
#   12. Critized by Government       -0.663
#   13. Under Government Crackdown   -1.010
